---
title: "GDaiess_STAT651_HW3"
author: "Gabriel Daiess TQ5979"
format: 
  html:
    self-contained: true
editor: visual
---

## Tableau Plot

https://public.tableau.com/views/GDaiess_STAT651_HW3/Dashboard1

## Ch. 17 Exercise 1

```{r}
library(tidyverse)
library(tibble)

EDM <- tibble(
  address = "Emily Dickinson Museum, Amherst, MA"
) |> 
  tidygeocoder::geocode(address, method = "osm")

library(leaflet)
EDMmap <- leaflet()  |>  
  addTiles() |> 
  addMarkers(data = EDM)
EDMmap

print(EDM[, c("lat", "long")])
```

## Ch. 18 Exercise 1

### a.

```{r}
library(mdsr)
library(pacman)
p_load(sf, tidygeocoder)
data("Violations")

#reduce the DF to only have columns of interest, save on computing speed
v1 <- Violations |> 
  select(camis, dba, building, street, zipcode) |> 
  unite(loc, building, street, sep = " ") |> 
  unite(loc, loc, zipcode, sep = ",") |> 
  distinct()

dim(v1)

#further cleanup because some addresses start with 0 or NA
v2 <- v1 |> 
  filter(!grepl("^[01]|NA", loc))

```

### test

```{r}
x <- v2 |> 
  sample_n(size = 20)

library(tictoc)
tic()
v2_loc <- x |> 
  geocode(loc, method = "osm")
toc()

v2_loc
```

Too many addresses to geocode, using a sample of 20 addresses I find that the latitudes and longitudes of the restaurants with violations in New York City range from approximately 40.6 to 40.8, and -73.7 to -73.9, respectively.

### b.

```{r}
# take small sample for visual
x2 <- v2 |> 
  sample_n(size = 80)

x2_geo <- x2 |> 
  geocode(loc, method = "osm") |>
  drop_na() |> 
  filter(long > -74, long < -73, lat > 40.5, lat < 41) |> 
  st_as_sf(coords=c("long","lat")) |>  
  st_set_crs(4326) 

library(ggspatial)
library(prettymapr)
ggplot(x2_geo) + 
  annotation_map_tile(type = "osm", zoomin = 0) +
  geom_sf(data = x2_geo, inherit.aes = FALSE) +
  coord_sf(crs = st_crs(4326))
```

### c.

```{r}
library(leaflet)
violation_map <- leaflet() |>  
  addTiles() |> 
  addMarkers(data = x2_geo)

violation_map
```

both maps do not include all unique 25,866 addresses in the violations, but instead a sample of 80 addresses across NYC, due to processing capabilities of my PC.

## Ch. 18 Exercise 2
### a
```{r}
library(macleish)
library(purrr)
boundary <- macleish_layers |> 
  pluck("boundary")
streams <- macleish_layers |> 
  pluck("streams")
buildings <- macleish_layers  |> 
  pluck("buildings")
trails <- macleish_layers |> 
  pluck("trails")
landmarks <- macleish_layers  |> 
  pluck("landmarks")

boundary_plot <- ggplot(boundary) +
  annotation_map_tile(type = "osm")
  geom_sf()
 

boundary_plot +
  geom_sf(data = streams, color = "blue3", size = 1.5) +
  geom_sf(data = buildings, color = "orange") +
  geom_sf(data = trails, color = "coral4", size = 1) +
  geom_sf(data = landmarks, color = "red") +
  scale_x_continuous(breaks = c(-72.677, -72.683))
```
## Ch. 18 Exercise 2
### b
```{r}
library(leaflet)
leaflet() |> 
  addTiles() |> 
  addPolygons(
    data = macleish_layers[["boundary"]], weight = 1) |> 
  addPolygons( data = macleish_layers[["buildings"]], weight = 1)  |> 
  addMarkers(data = filter(macleish_layers[["landmarks"]], 
                           grepl("Met", Label)),popup = ~Label)  |>  
  addPolylines(data = macleish_layers[["trails"]], weight = 1) |>  
  addPolylines(data = macleish_layers[["streams"]],weight = 1)
```




















